\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation.

\section{Team Meeting Attendance}

\wss{For each team member how many team meetings have they attended over the
time period of interest.  This number should be determined from the meeting
issues in the team's repo.  The first entry in the table should be the total
number of team meetings held by the team.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 6\\
Housam & 6 \\
Rachid & 6 \\
Sufyan & 6 \\
Taaha & 6 \\
Omar & 6 \\
\bottomrule
\end{tabular}
\end{table}


\section{Supervisor/Stakeholder Meeting Attendance}

\wss{For each team member how many supervisor/stakeholder team meetings have
they attended over the time period of interest.  This number should be determined
from the supervisor meeting issues in the team's repo.  The first entry in the
table should be the total number of supervisor and team meetings held by the
team.  If there is no supervisor, there will usually be meetings with
stakeholders (potential users) that can serve a similar purpose.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 1\\
Housam & 0 \\
Rachid & 1 \\
Sufyan & 1 \\
Taaha & 1 \\
Omar & 1 \\
\bottomrule
\end{tabular}
\end{table}

Housam missed the supervisor meeting held between rev 0 and the final documentation due other obligations.

\section{Lecture Attendance}


\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Housam & 1 \\
Rachid & 1 \\
Sufyan & 1 \\
Taaha & 0 \\
Omar & 0 \\
\bottomrule
\end{tabular}
\end{table}

\wss{Some lectures missed but at least one group member attended each of the lectures this semester.}

\section{TA Document Discussion Attendance}

\wss{For each team member how many of the informal document discussion meetings
with the TA were attended over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Housam & 1 \\
Rachid & 1 \\
Sufyan & 1 \\
Taaha & 1 \\
Omar & 1 \\
\bottomrule
\end{tabular}
\end{table}

\wss{All member were in attendace. Rachid and Sufyan in person, rest virtual.}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 155 & 100\% \\
Housam & 44 & 28.4\% \\
Taaha & 16 & 10.3\% \\
Omar & 35 & 23.0\% \\
Sufyan & 17 & 11.0\% \\
Rachid & 43 & 27.7\% \\
\bottomrule
\end{tabular}
\end{table}

\section{Issue Tracker}

\wss{For each team member how many issues have they authored (including open and
closed issues (O+C)) and how many have they been assigned (only counting closed
issues (C only)) over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Housam & 8 & 1 \\
Rachid & 0 \\
Sufyan & 0 \\
Taaha & 0 \\
Omar & 0 \\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\section{Team Charter Trigger Items}

\textbf{Quantified Triggers:}
\begin{itemize}
  \item Full attendance expected at weekly meetings.
  \item Members are expected to communicate absences and progress updates.
  \item A target number of commits set informally, with highest contributor rewarded.
  \item Bi-weekly team building meetups planned.
\end{itemize}

\textbf{Violations:}
\begin{itemize}
  \item One member missed the supervisor meeting.
  \item Some members had low commit counts relative to others.
  \item Not all bi-weekly meetups were held consistently due to scheduling conflicts.
\end{itemize}

\textbf{Plan to Address Violations:}
\begin{itemize}
  \item Improve calendar coordination and reminders for supervisor and team events.
  \item Encourage more even commit distribution in final stages of the project.
  \item Continue open communication and support to maintain engagement.
\end{itemize}


\wss{If your team has additional metrics of productivity, please feel free to
add them to this report.}

\end{document}