\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: POC\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member up to the POC
Demo.  The time period of interest is the time between the beginning of the term
and the POC demo.

\section{Demo Plans}

We will be demonstrating the preliminary creation of our website, we hope to showcase the ability for users to login, upload and be notified by the application depending on the reimbursement request. The back-end and front-end will be skeletons of the final build but will still be functionally working. 

\section{Team Meeting Attendance}

\wss{For each team member how many team meetings have they attended over the
time period of interest.  This number should be determined from the meeting
issues in the team's repo.  The first entry in the table should be the total
number of team meetings held by the team.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 8\\
Omar & 8\\
Sufyan & 8\\
Taaha & 8\\
Housam & 8\\
Rachid & 8\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.} \\
We did not track our meeting issues in the team repo unfortunately, all of our calls were held in our private discord server. However, moving forward we will make an effort to track all team activities on Git as well. 

\section{Supervisor/Stakeholder Meeting Attendance}

\wss{For each team member how many supervisor/stakeholder team meetings have
they attended over the time period of interest.  This number should be determined
from the supervisor meeting issues in the team's repo.  The first entry in the
table should be the total number of supervisor and team meetings held by the
team.  If there is no supervisor, there will usually be meetings with
stakeholders (potential users) that can serve a similar purpose.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 3\\
Omar & 3\\
Sufyan & 3\\
Taaha & 3\\
Housam & 3\\
Rachid & 3\\
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}
We call our supervisor for important milestone discussion, we will begin to call more for more feedback based on the website. 
\section{Lecture Attendance}

\wss{For each team member how many lectures have they attended over the time
period of interest.  This number should be determined from the lecture issues in
the team's repo.  The first entry in the table should be the total number of
lectures since the beginning of the term.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 26\\
Omar & 17/26\\
Sufyan & 19/26\\
Taaha & 18/26\\
Housam & 19/26\\
Rachid & 17/26\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the lecture attendance can be provided here.}
We usually try to go to lectures as a team, just to make sure we are all on the same page during the project. 
\section{TA Document Discussion Attendance}

\wss{For each team member how many of the informal document discussion meetings
with the TA were attended over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 3\\
Omar & 2\\
Sufyan & 2\\
Taaha & 2\\
Housam & 2\\
Rachid & 2\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the attendance can be provided here.}
We all missed one meeting for the VnV report due to unexpected circumstances, we hope to continue to meet for the upcoming milestones. 
\section{Commits}

\wss{For each team member how many commits to the main branch have been made
over the time period of interest.  The total is the total number of commits for
the entire team since the beginning of the term.  The percentage is the
percentage of the total commits made by each team member.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 136 & 100\% \\
Omar & 16 & 12\% \\ 
Sufyan & 33 & 24\% \\  
Taaha & 24 & 18\% \\  
Housam & 42 & 31\% \\  
Rachid & 21 & 15\% \\  
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.  For
instance, if a team member has more commits to unmerged branches, these numbers
can be provided here.  If multiple people contribute to a commit, git allows for
multi-author commits.}

\section{Issue Tracker}

\wss{For each team member how many issues have they authored (including open and
closed issues (O+C)) and how many have they been assigned (only counting closed
issues (C only)) over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Omar & 4 & 0 \\
Sufyan & 5 & 0 \\
Taaha & 5 & 1 \\
Housam & 6 & 2 \\
Rachid & 6 & 0 \\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}
Most issues have been closed yet, but when we revise and update our previous documents we will go through all of the issues. 
\section{CICD}

To ensure consistent quality within our project, we will use a CICD pipeline integrated with GitHub Actions. Our CICD strategy focuses on:

\begin{itemize}
    \item \textbf{Automated Testing and Linting}: Every time a commit is pushed to the repository, GitHub Actions will automatically multiple checks, including running unit tests, integration tests, and linting checks. This will help us catch errors early in the development cycle, ensuring code quality and reducing bugs.

    \item \textbf{PDF Build Automation for Documentation}: Whenever a change is made to any LaTeX file in the repository, GitHub Actions will automatically compile the updated LaTeX document to PDF. This ensures that our documentation is always up-to-date and accessible in PDF format. If the build fails, team members will receive an alert, allowing them to address any issues immediately.

    \item \textbf{Automated Deployment to Staging Environment}: For every change that is pushed to the main branch, GitHub Actions will deploy the latest version of the application to a staging environment. This will allow the team and stakeholders to review and test features. 

    \item \textbf{Version Control and Release Management}: At each major project milestone, GitHub Actions will assist in creating a tagged release. This includes an archived version of the code, documentation, and any necessary deployment instructions, providing a clear record of progress.

\end{itemize}

\end{document}